---
title: "Presentation"
author: "Aaron Schram"
date: "11/28/2021"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Biographical

- Hello, I am Aaron Schram. My birthday is February 13th. I grew up in zimmerman, Minnesota.
- Program: Joint MS/PHD Statistics
- Graduation Date: Spring 2023

## Favorite Animal

```{r picture, echo = TRUE}
library("jpeg")

x <- "https://www.rainforest-rescue.org/photos/article/facebook/fb/en/flughund-mauritius.jpg"

download.file(x,'x.jpg', mode = 'wb')
jj <- readJPEG("x.jpg",native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)


```



## Slide with R Output

```{r palmerpenguins, echo = TRUE}
if (!"palmerpenguins" %in% installed.packages()) {
  remotes::install_github("allisonhorst/palmerpenguins")
}
library(palmerpenguins)
library(ggplot2)
```

## Slide with Plot

```{r penguins}
ggplot(penguins, aes(x = body_mass_g, y = bill_length_mm, z=flipper_length_mm, color = sex)) + 
  geom_point()+
  scale_color_manual(values = c("male" = "Pink",
                               "female" = "blue")) + 
  geom_text(aes(label=species),hjust=0, vjust=0) +
  geom_line()+coord_polar()+theme_classic()+
  xlab("Body Mass") + ylab("Bill Length") + ggtitle("Penguin Body Mass by Bill Length Polar Plot")
```

## CV Link
https://www.overleaf.com/read/mmrmjqjytrxd
